Modal Abstractions for Virtualizing Memory Addresses

### 2023-04-04 programlogic.tex
+

\begin{remark}[Exchanging Page-Table-Walk-Summarization Mappings (Tokens) ]
  $\mathcal{A}\textsf{PTableWalk}$'s fragmental-ownership represents an individual key-value pair (per-virtual-address) which can be handled as a \textit{look-up} resource for an individual virtual address.
  To build more intuition on the convenience of this protocol, we can think of the use-case \textit{unmapping-pages} as collecting the fragmental map pairs, e.g. $\sumwalkabs\vaddr\qfrac\paddr$, from collecting the assertions, removing them from the ghost map, and then updating the page tables.
\end{remark}
\begin{figure*}
\[
\begin{array}{l}
    \vaddr\mapsto_{\textsf{v}}\{\textsf{q}\}\vpage \stackrel{\triangle}{=} 
    \exists \entryo \ldotp
    \sumapaces\crthree\delta \ast 
  \sumwalkabs\vaddr\qfrac\paddr \ast 
   \nfpointsto{\mask\vaddr\ft\entryo}{\mask\vaddr\tw\entryo}\vpage\qfracone\naddr
\end{array}
\]
\caption{Virtual-Pointsto for Sharing Pages}
  \label{fig:virtualpointstosharing}
\end{figure*}
%\subsection{Address-Space Abstraction}
%\label{sec:aspacemodal}

@@

   \includegraphics[width=0.75\columnwidth]{logical_addr_space.png}
  \caption{Logical Resources of Address-Space Abstraction}
  \label{fig:logicaladdrspace}
    \subsubsection{Global Per-Address-Space Invariant}
    \label{sec:peraspaceinvariant}
    Virtual points-to assertions would need to be defined in terms of physical points-to assertions and hardware-specific address translation assertions for mapped virtual addresses ($\textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}(\crthree,\entryf,\entrytr,\entrytw,\entryo)$ in Figure \ref{fig:peraspaceinvariant}). For each virtual address \textit{mapped} with a physical page table entry, abstracted with ghost mappings ($\sumwalkabs\vaddr\qfrac\paddr$) in virtul-pointsto relations as shown in Figure \ref{fig:virtualpointstosharing}), there exsits a physical page table walk.  
    \[ \bigast{(\vaddr, \entryo)\in \ptablestore}{\exists\;(\entryf\;,\entrytr\;,\entrytw)\ldotp \textsf{L}_{4}\_\textsf{L}_{1}\_\textsf{PointsTo}(\vaddr,\crthree,\entryf,\entrytr,\entrytw,\entryo)} \]
    By separating the virtual-points Overlapping address spaces — both shared data, and shared page tables
which may see updates — can be coordinated with protocols to ensure those updates preserve
address space invariants.

@@

>>>>

\begin{remark}[Exchanging Page-Table-Walk-Summarization Mappings (Tokens) ]
  $\mathcal{A}\textsf{PTableWalk}$'s fragmental-ownership represents an individual key-value pair (per-virtual-address) which can be handled as a \textit{look-up} resource for an individual virtual address.
  To build more intuition on the convenience of this protocol, we can think of the use-case \textit{unmapping-pages} as collecting the fragmental map pairs, e.g. $\sumwalkabs\vaddr\qfrac\paddr$, from collecting the assertions, removing them from the ghost map, and then updating the page tables. while Besides, y separating the virtual-points Overlapping address spaces — both shared data, and shared page tables
which may see updates — can be coordinated with protocols to ensure those updates preserve
address space invariants.
\end{remark}
\begin{figure*}
\[
\begin{array}{l}
    \vaddr\mapsto_{\textsf{v}}\{\textsf{q}\}\vpage \stackrel{\triangle}{=} 
    \exists \entryo \ldotp
    \sumapaces\crthree\delta \ast 
  \sumwalkabs\vaddr\qfrac\paddr \ast 
   \nfpointsto{\mask\vaddr\ft\entryo}{\mask\vaddr\tw\entryo}\vpage\qfracone\naddr
\end{array}
\]
\caption{Virtual-Pointsto for Sharing Pages}
  \label{fig:virtualpointstosharing}
\end{figure*}
%\subsection{Address-Space Abstraction}
%\label{sec:aspacemodal}

@@

\begin{figure}
   \includegraphics[width=0.75\columnwidth]{logical_addr_space.png}
  \caption{Logical Resources of Address-Space Abstraction}
  \label{fig:logicaladdrspace}
  \end{figure}

@@

 \[\mathcal{A}\textsf{spaces} \stackrel{\triangle}{=} \textsc{Auth} (\; \mathcal{W}_{64} \;\rightarrow_{\textrm{fin}} \; (\textsc{Agree } \mathsf{GName},\mathord{=}) ) \]
